Associative Data Structures for Website Filtering

### 2014-04-17 paper/paper.tex
Rewrote plan.

    In this paper, we attempt to answer these questions. Section~\ref{sec:plan} provides details
    about our research plan and the scopes of our research. Section~\ref{sec:implementation} is
    about the implementation of our setup in C++.  The rest of the paper states our results and the
    conclusions that can be drawn from them.

@@

    \subsubsection*{Scope and assumptions}

    We make several assumptions for our research.

    Firstly we plan on only working with datasets that are certain to fit into the main memory of our machine. We intend to
    purely examine the relative speed and memory-efficiency of the different data structures. Using datasets larger than
    memory will cause regular lookups to the harddrive, which we assume would skew our results.

    In order to make the measurements more predictable, we will always ensure that insertions are only performed with
    non-existent keys. The alternative would make either the memory usage or number of insertions non-deterministic, which
    could cause inaccuracies in measurement. Similarly, we require that all queries be performed on existing keys.

    To mimic real usage, we will insert and then access the keys in an arbitrary order.  However, we will keep the order consistent
    between tests on different data structures.  Together this will minimize any bias related to any kind of order-dependent
    performance, which would likely be an advantage specific to the implementation, not to the data structure. We will
    generate the order for both lookup and insertion by shuffling the dataset we chose for the specific test. This means that
    orders will not be persistent between different data set sizes; however, we do not expect this to be significant.

    We realize that methods to measure the amount of time required for actions will themselves need time. We will however
    use the same time-measuring method for all data structures, so we can still use the results to compare the different
    data structures.

@@

    We used C++ implementations of the data structures involved, and also the language for our
    measuring code.  We chose C++ as it is an industry standard\footnote{ref}, provides the
    necessary tools, and does not carry the risk of garbage collection pauses or effects due to
    ``warming-up time''.

>>>>

    In this paper, we attempt to answer these questions. Section~\ref{sec:plan} provides details
    about the plan and scope of our research. Section~\ref{sec:implementation} is about the
    implementation of our setup in C++.  The rest of the paper states our results and the
    conclusions that can be drawn from them.

@@

    We set out to collect experimental data about three performance characteristics of the data
    structures we selected: insertion speed, query speed, and memory usage.  We would start by
    writing code that performed the necessary measurements, run it repeatedly to find the average
    and standard error, and then perform statistical analysis on the results.

    In order to perform the tests we would require a set of keys for every key type.  For IP
    addresses, consecutive integers starting from 0 would be used.  For domain names and full paths,
    we wanted to simulate more realistic data.  We would use a word list and a list of top level
    domains and use possible combinations of elements of each as our domains.  For full paths, we
    would take some number of domains and append random strings of a fixed length to simulate
    resource identifiers such as used by YouTube and Google Drive.  In the latter case, we wanted
    the number of paths per domain to be relatively high, as we expected filtered webpages to be
    more likely to belong to the same site.  Therefore, instead of taking all possible combinations,
    we first took a subset of our list of domains and only then added random strings.

    When running our tests, we would take some subset of the set involved and measure the time it
    took to run an insert or query using each element of that subset.  Queries and inserts would not
    be mixed, and each element would be queried and inserted exactly once.  The map to be queried
    against would contain exactly the elements of the subset.  All in all, this would allow us to
    compensate for issues that could occur due to particular orders having particular performance
    characteristics, while not disturbing measurements in ways that a stochastic element count
    likely would.

    We would ensure that all subset fit in main memory, as the alternative would significantly
    favour data structures that used less memory.  Furthermore, we would perform all time
    measurements repeatedly and then take the average in order to decrease the influence of timing
    overhead.

@@

    We used C++ implementations of the data structures involved, and also used the language for our
    measuring code.  We chose C++ as it is an industry standard\footnote{ref}, provides the
    necessary tools, and does not carry the risk of garbage collection pauses or effects due to
    ``warming-up time''.
